CS6213 Project Report

### 2021-05-07 report/paper.tex
Report: WIP scope

\documentclass[a4paper]{article}
% \usepackage[margin=1.5in]{geometry}
\usepackage{fontspec}
\usepackage{csquotes}
\usepackage[hidelinks]{hyperref}
\usepackage[backend=biber, style=alphabetic]{biblatex}
\usepackage{lastpage}
\usepackage{xspace}
\usepackage{paralist}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{mathtools}
\usepackage{lipsum}
\usepackage[svgnames]{xcolor}
\usepackage{caption}
\usepackage{subcaption}

@@

\title{Project Report}
\author{George Pîrlea \and Darius Foo}
\date{\today}

@@

>>>>

\documentclass[a4paper]{article}
% \usepackage[margin=1.5in]{geometry}
\usepackage{fontspec}
\usepackage{csquotes}
\usepackage[hidelinks]{hyperref}
\usepackage[backend=biber, style=alphabetic]{biblatex}
\usepackage{lastpage}
\usepackage{xspace}
\usepackage{paralist}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{mathtools}
\usepackage{lipsum}
\usepackage[svgnames]{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}

@@

\title{CS6213 Project Report}
\author{George Pîrlea \and Darius Foo}
\date{\today}

@@

\section{Project Scope}

We set out to answer the following research questions:

\begin{enumerate}[label={(Q\arabic*)}]
    \item \textbf{Conformance testing.} Given a TLA model that satisfies some simple properties and a system implementation, what is the easiest way to check that the implementation satisfies the properties?

    \item \textbf{Refinement mappings.} Given a model and an implementation, how can we best define the correspondence between the two, perhaps via a combination of manual/inferred annotations?

    \item \textbf{Empirical evaluation of conformance.} For real-world distributed systems that come with both TLA models and implementations, empirically, is there a correspondence between the model and the implementation?
\end{enumerate}
